---
title: "hospital"
author: "Jingning Yang"
date: "3/24/2020"
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Background

Designing an impact evaluation study as part of DrPH dissertation. Study is located in Lagos Nigeria.
The overall study is a concurrent mixed-methods study that combines a quasi-experimental controlled before/after design with qualitative methods.

Focus on the quality of four cares,  Antenatal Care (ANC), Febrile under 5 children,  Hypertension and Diabetes

This study will utilize a two stage stratified random sampling technique to select health facilities. Six strata will be created using the following criteria: ownership (public versus private), facility type (primary versus secondary), and size (based on annual outpatient patient volume: low versus high volume facilities). Seven health facilities will be randomly selected within each stratum and in cases where only one facility is available in a stratum, that facility will be automatically selected


## Client's requests

1. What are the pros and cons of framing the outcome measures as proportion as against a continuous variable?
2. What are the options for calculating sample size?
3. What are the approaches to thinking about secondary outcomes regarding power and sample size?
4. Does my plan to use propensity score matching impact my sample size calculation?

## Power calculation
Since this study utilize a two stage stratified random sampling technique to select health facilities, we used "samplesize_mixed()" to computes an approximated sample size for linear mixed models(two-level-designs).
```{r}
# Sample size for multilevel model with 4 cluster groups and a small to
# medium effect size (Cohen's d) of 0.1. 
library(sjstats)
library(lme4)
samplesize_mixed(eff.size = .1, k = 4) #k = 4??
#smpsize_lmm(eff.size = .1, k = 4) #same as above
#> $`Subjects per Cluster`
#> [1] 785
#> $`Total Sample Size`
#> [1] 3141
#785 subjects per cluster and hence a total sample size of about 3141 observations is needed.

# Sample size for multilevel model with 4 cluster groups and a medium
# to large effect size for linear models of 0.1. Five subjects per cluster and
# hence a total sample size of about 107 observations is needed.
samplesize_mixed(eff.size = .1, k = 4, power = .8, n = 7)
#smpsize_lmm(eff.size = .1, df.n = 7, k = 4, power = .8) #same as above
#> $`Subjects per Cluster`
#> [1] 33
#> 
#> $`Total Sample Size`
#> [1] 134
```


