---
title: "report"
author: "Jingning Yang, Yanwen Liu, He Guo"
date: "2/21/2020"
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
library(tidyverse)
library(readxl)
library(dplyr)
library(nnet)
library(rlist)
library(arm)
library(knitr)
library(MASS)
library(ggpubr)
theme_set(theme_pubr())
# loading packages
```

# Introduction
Our client, Reshma Satish, a PhD student at Boston University's Department of Forensic Anthropology,administered a project involves fracturing 135 long deer bones using a standardized fracturing apparatus over a period of 540 days. The bones are broken into 9 groups with 15 bones in each group and each group is fractured at different times(0 days,30 days,60 days,90 days,180 days,270 days, etc.) Her goal was to investigate how time of exposure of long bones affects variables such as the type of fracture angle, the type of fracture surface morphology,etc.that is created on the bones. Currently, our client only has data until day 270 since this experiment still keep going.

This report will start with a description of the EDA, as well as Data analysis/Data structure. Then we will describe the methods we will use on modeling part, followed by our analysis.

# Data Cleaning and EDA

## Data structure

We are provided the data in an excel document with 7 groups of drying days and a total of 105 bones. There are 10 variables in the dataset, but we will only focus on 8 of them, with Bisect Fracture and Fracture-like as binary responses, Number of fragments as a numerical response, and Fracture Angle, Fracture Type, Fracture Surface, Fracture Outline, and Fractographic Features as unordered categorical responses. 

## Data Cleaning
```{r,echo=F}
bone <- readxl::read_xlsx("BU Thesis Data.xlsx", sheet = 2)
drop<-c()
for (i in 1:nrow(bone))  {
  if (is.na(bone$`Bone Type`[i])){
    drop <- c(drop, i)
  }
}
bone<-bone[-drop,]
# read bone and drop the date without information
# ignore unobserved bone
bone <- dplyr::select(bone,-`Bone Type`,-`Percentage of Feature Present`)
# select columns from Bone Type to Percentage of Feature Present
bone$`Bone Specimen` <- gsub("\\,.*","", bone$`Bone Specimen`)
bone$`Bone Specimen` <- gsub("[^0-9]","", bone$`Bone Specimen`)
bone$`days`<-as.numeric(bone$`Bone Specimen`)
bone<-mutate(bone,`Bone Specimen`=fct_relevel(`Bone Specimen`,'0','30','60','90','180','270','360'))
# creating variable drying day
typeof(bone$`Bone Specimen`)
bone$`Fractographic Features`[bone$`Fractographic Features`=="N/A"]<-"No Feature"
bone$`Fracture Angle`[bone$`Fracture Angle`=="N/A"]<-"non applicable"
bone$`Fracture Type`[bone$`Fracture Type`=="N/A"]<-"non applicable"
bone$`Fracture Surface`[bone$`Fracture Surface`=="N/A"]<-"non applicable"
bone$`Fracture Outline`[bone$`Fracture Outline`=="N/A"]<-"non applicable"
#Clean dependent variable
bone$`Bisecting Fracture`<-factor(bone$`Bisecting Fracture`)
bone$`Fracture-like`<-factor(bone$`Fracture-like`)
bone$`Fracture Angle`<-factor(bone$`Fracture Angle`)
bone$`Fracture Type`<-factor(bone$`Fracture Type`)
bone$`Fracture Surface`<-factor(bone$`Fracture Surface`)
bone$`Fracture Outline`<-factor(bone$`Fracture Outline`)
bone$`Fractographic Features`<-factor(bone$`Fractographic Features`)
# transfer variables to factor 
```
At a first glance of the raw dataset, there are many NA inputs. After discussed with our client, we decide to  change NA in Fracture Angle, Fracture Type, Fracture Surface, and Fracture Outline to non applicable and change NA in Fractographic Features to No Feature. Moreover, we create numerical variable drying days from variable Bone Specimen for future analysis.

##Create Dummy Variable

There are some observation have multiple feature in Fractographic Features variable.  Then, we create 6 dummy variable to indicate which feature appaer for a given observation. 
```{r}
bone$`WAKE HACKLE`<-rep(0,nrow(bone))
bone$`WAKE HACKLE`[grepl('WAKE HACKLE', bone$`Fractographic Features`)]<-1
bone$`WAKE HACKLE`<-as.factor(bone$`WAKE HACKLE`)

bone$`BONE HACKLE`<-rep(0,nrow(bone))
bone$`BONE HACKLE`[grepl('BONE HACKLE', bone$`Fractographic Features`)]<-1
bone$`BONE HACKLE`<-as.factor(bone$`BONE HACKLE`)

bone$`BONE MIRROR`<-rep(0,nrow(bone))
bone$`BONE MIRROR`[grepl('BONE MIRROR', bone$`Fractographic Features`)]<-1
bone$`BONE MIRROR`<-as.factor(bone$`BONE MIRROR`)

bone$`CANTILEVER CURL`<-rep(0,nrow(bone))
bone$`CANTILEVER CURL`[grepl('CANTILEVER CURL', bone$`Fractographic Features`)]<-1
bone$`CANTILEVER CURL`<-as.factor(bone$`CANTILEVER CURL`)

bone$`ARREST RIDGE`<-rep(0,nrow(bone))
bone$`ARREST RIDGE`[grepl('ARREST RIDGE', bone$`Fractographic Features`)]<-1
bone$`ARREST RIDGE`<-as.factor(bone$`ARREST RIDGE`)

bone$`WALLNER LINES`<-rep(0,nrow(bone))
bone$`WALLNER LINES`[grepl('WALLNER LINES', bone$`Fractographic Features`)]<-1
bone$`WALLNER LINES`<-as.factor(bone$`WALLNER LINES`)
```

## EDA (need revise, add explanation & change Fractographic features into 6 dummy varaibles.)
We conduct a basic exploratory data analysis (EDA) to visualize the data and find some patterns between variables. We focus on the two binary responses, Number of fragments, and the Fractographic Features as well.
```{r,echo=F}
options(digits = 2) 
table1<-rbind(table(bone$`Bisecting Fracture`,bone$`Bone Specimen`)[2,]/15,table(bone$`Fracture-like`,bone$`Bone Specimen`)[2,]/15)
row.names(table1)<-c('Bisecting percentage','Fracture-like percentage')
kable(table1,caption = 'Bisecting Fracture and Fracture-like percentage for different drying-day groups')
ggplot(data = bone, mapping = aes(x = `Bone Specimen`, y = `Number of Fragments`)) + geom_boxplot()+labs(x="Drying Days")


WAKE_HACKLE<-ggplot(data = bone) + geom_bar(mapping = aes(x = `Bone Specimen`, fill = `WAKE HACKLE`))+labs(x="Drying Days")

BONE_HACKLE<-ggplot(data = bone) + geom_bar(mapping = aes(x = `Bone Specimen`, fill = `BONE HACKLE`))+labs(x="Drying Days")

BONE_MIRROR<-ggplot(data = bone) + geom_bar(mapping = aes(x = `Bone Specimen`, fill = `BONE MIRROR`))+labs(x="Drying Days")

CANTILEVER_CURL<-ggplot(data = bone) + geom_bar(mapping = aes(x = `Bone Specimen`, fill = `CANTILEVER CURL`))+labs(x="Drying Days")

WALLNER_LINES<-ggplot(data = bone) + geom_bar(mapping = aes(x = `Bone Specimen`, fill = `WALLNER LINES`))+labs(x="Drying Days")

ARREST_RIDGEL<-ggplot(data = bone) + geom_bar(mapping = aes(x = `Bone Specimen`, fill = `ARREST RIDGE`))+labs(x="Drying Days")

figure.1 <- ggarrange(WAKE_HACKLE, BONE_HACKLE, BONE_MIRROR,CANTILEVER_CURL,WALLNER_LINES,ARREST_RIDGEL,
                    ncol = 2, nrow = 3)
figure.1

```


# Modeling & Interpretation (YW-poisson) (HG-fracture type & surface)

We used logistic regression, poisson regression, and multinomial logit model based on different types of response variables in our dataset.

## Fracture Type


###COMMINUTED relative to BUTTERFULY:
  
Intercept:  This is the multinomial logit estimate for COMMINUTED relative to BUTTERFULY when the predictor variables in the model are evaluated at zero. For day equals to zero, the logit for preferring COMMINUTED relative to BUTTERFULY is 0.8269632. Note that evaluating days equals to zero indicated that the day of starting  the experiment
Days:  This is the multinomial logit estimate for a one unit increase in Days for COMMINUTED relative to BUTTERFULY.  If a subject were to increase Days  by one point, the multinomial log-odds of preferring COMMINUTED relative to BUTTERFULY would be expected to Increase by 10.00216.

T-statistics for days in Log(Prob(COMMINUTED)/Prob(BUTTERFULY)) equals to  0.8158939, which is lower than 2.  Then, the Days does not make any difference for log-odds of preferring COMMINUTED relative to BUTTERFULY

###non applicable relative to BUTTERFULY


Intercept:  This is the multinomial logit estimate for non applicable relative to BUTTERFULY when the predictor variables in the model are evaluated at zero. For day equals to zero, the logit for preferring non applicable relative to BUTTERFULY is1.5166589. Note that evaluating days equals to zero indicated that the day of starting the experiment
Days: This is the multinomial logit estimate for a one unit increase in Days for non applicable relative to BUTTERFULY.  If a subject were to increase Days  by one point, the multinomial log-odds of preferring non applicable relative to BUTTERFULY would be expected to decrease by  0.0024548581.

T-statistics for days in Log(Prob(non applicable)/Prob(BUTTERFULY)) equals to | -0.0024548581/0.002647403| = 0.8948441, which is lower than 2.  Then, the Days does not make any difference for log-odds of preferring non applicable relative to BUTTERFULY

Log(Prob(OBLIQUE)/Prob(BUTTERFULY)) = -0.1913727 -0.0027752170*Days

### OBLIQUE relative to BUTTERFULY:

Intercept:  This is the multinomial logit estimate for OBLIQUE relative to BUTTERFULY when the predictor variables in the model are evaluated at zero. For day equals to zero, the logit for preferring OBLIQUE relative to BUTTERFULY is-0.1913727. Note that evaluating days equals to zero indicated that the day of starting the experiment
Days:  This is the multinomial logit estimate for a one unit increase in Days for OBLIQUE relative to BUTTERFULY.  If a subject were to increase Days  by one point, the multinomial log-odds of preferring OBLIQUE relative to BUTTERFULY would be expected to decrease by 0.0027752170.

T-statistics for days in Log(Prob(OBLIQUE)/Prob(BUTTERFULY)) equals to | -0.0027752170
/ 0.004192975| = 0.661873, which is lower than 2.  Then, the Days does not make any difference for log-odds of preferring OBLIQUE relative to BUTTERFULY

Log(Prob(SEGMENTAL)/Prob(BUTTERFULY)) = -0.5994698 -0.0006693986*Days

###SEGMENTAL relative to BUTTERFULY:

Intercept: This is the multinomial logit estimate for SEGMENTAL relative to BUTTERFULY when the predictor variables in the model are evaluated at zero. For day equals to zero, the logit for preferring SEGMENTAL relative to BUTTERFULY is-0.5994698. Note that evaluating days equals to zero indicated that the day of starting the experiment
Days: This is the multinomial logit estimate for a one unit increase in Days for SEGMENTAL relative to BUTTERFULY.  If a subject were to increase Days  by one point, the multinomial log-odds of preferring SEGMENTAL relative to BUTTERFULY would be expected to decrease by -0.0006693986.

T-statistics for days in Log(Prob(SEGMENTAL)/Prob(BUTTERFULY)) equals to | -0.0006693986/0.004110398| = 0.1628549, which is lower than 2.  Then, the Days does not make any difference for log-odds of preferring SEGMENTAL relative to BUTTERFULY.

Log(Prob(TRANSVERSE)/Prob(BUTTERFULY)) = -1.9804151 -0.004371236*Days

###TRANSVERSE relative to BUTTERFULY:

Intercept : This is the multinomial logit estimate for TRANSVERSE relative to BUTTERFULY when the predictor variables in the model are evaluated at zero. For day equals to zero, the logit for preferring TRANSVERSE relative to BUTTERFULY is -1.9804151. Note that evaluating days equals to zero indicated that the day of starting the experiment
Days: This is the multinomial logit estimate for a one unit increase in Days for TRANSVERSE relative to BUTTERFULY.  If a subject were to increase Days  by one point, the multinomial log-odds of preferring TRANSVERSE relative to BUTTERFULY would be expected to decrease by 0.004371236.

T-statistics for days in Log(Prob(TRANSVERSE)/Prob(BUTTERFULY)) equals to | -0.0043712363/0.010436283 | =0.4188499, which is lower than 2.  Then, the Days does not make any difference for log-odds of preferring TRANSVERSE relative to BUTTERFULY

According to the Binned residual plot, there is not clearly pattern. 
```{r}
fit.Fracture_Type<-multinom(bone$`Fracture Type`~bone$days,trace = FALSE)
summary(fit.Fracture_Type)
binnedplot(fitted(fit.Fracture_Type),resid(fit.Fracture_Type,type="response"))
```

```{r}
t_stat_type <- summary(fit.Fracture_Type)$coefficients / summary(fit.Fracture_Type)$standard.errors
t_stat_type
```

## Fracture Surface

###non applicable relative to INTERMEDIATE:

Log(Prob(non applicable)/Prob(INTERMEDIATE))= 2.185304 -0.008706689*Days

Intercept: This is the multinomial logit estimate for non applicable relative to INTERMEDIATE when the predictor variables in the model are evaluated at zero. For day equals to zero, the logit for preferring non applicable relative to INTERMEDIATE is 2.185304. Note that evaluating days equals to zero indicated that the day of starting the experiment
Days: This is the multinomial logit estimate for a one unit increase in Days for non applicable relative to INTERMEDIATE.  If a subject were to increase Days  by one point, the multinomial log-odds of preferring non applicable relative to INTERMEDIATE would be expected to decrease by 0.008706689.

T-statistics for days in Log(Prob(non applicable)/Prob(INTERMEDIATE)) equals to | 0.008706689/0.002536340| = 3.432777, which is greater than 2.  Then, the Days make a significant difference for log-odds of preferring non applicable relative to INTERMEDIATE

###ROUGH relative to INTERMEDIATE:

Log(Prob(ROUGH )/Prob(INTERMEDIATE))= -23.616556 + 0.060230466*Days

Intercept:  This is the multinomial logit estimate for ROUGH relative to INTERMEDIATE when the predictor variables in the model are evaluated at zero. For day equals to zero, the logit for preferring ROUGH relative to INTERMEDIATE is -23.616556. Note that evaluating days equals to zero indicated that the day of starting the experiment
Days: This is the multinomial logit estimate for a one unit increase in Days for ROUGH relative to INTERMEDIATE.  If a subject were to increase Days  by one point, the multinomial log-odds of preferring ROUGH relative to INTERMEDIATE would be expected to increase by 0.060230466.

T-statistics for days in Log(Prob(ROUGH)/Prob(INTERMEDIATE)) equals to |0.060230466/0.002940204 | = 20.48513, which is greater than 2.  Then, the Days make a significant difference for log-odds of preferring ROUGH relative to INTERMEDIATE

###SMOOTH relative to INTERMEDIATE:

Log(Prob(SMOOTH)/Prob(INTERMEDIATE))= 2.255591-0.007492372*Days

Intercept:  This is the multinomial logit estimate for SMOOTH relative to INTERMEDIATE when the predictor variables in the model are evaluated at zero. For day equals to zero, the logit for preferring SMOOTH relative to INTERMEDIATE is 2.255591. Note that evaluating days equals to zero indicated that the day of starting the experiment
Days:  This is the multinomial logit estimate for a one unit increase in Days for SMOOTH relative to INTERMEDIATE.  If a subject were to increase Days  by one point, the multinomial log-odds of preferring SMOOTH relative to INTERMEDIATE would be expected to decrease by 0.007492372.

T-statistics for days in Log(Prob(SMOOTH)/Prob(INTERMEDIATE)) equals to |-0.007492372/0.002378579| = 3.149936, which is greater than 2.  Then, the Days make a significant difference for log-odds of preferring SMOOTH relative to INTERMEDIATE


According to the Binned residual plot, there is not clearly pattern. 
```{r}
fit.Fracture_Surface<-multinom(bone$`Fracture Surface`~bone$days,trace = FALSE)
summary(fit.Fracture_Surface)
binnedplot(fitted(fit.Fracture_Surface),resid(fit.Fracture_Surface,type="response"))
```

```{r}
t_stat_Surface <- summary(fit.Fracture_Surface)$coefficients / summary(fit.Fracture_Surface)$standard.errors
t_stat_Surface
```

### Bisect Fracture
Since response variable "bisect fracture" is a binary outcomes(0 or 1), we are using logistic regression to figure out relationship between the probability of "bisect fracture" and value of "days".         
In addition, when "bisect fracture" is 0, it means the bone did not break by the standard fracturing machine, otherwise, it means the bone broke by the machine.        
```{r}
fit.Bisect_Fracture<-glm(bone$`Bisecting Fracture`~bone$days,family = binomial())
summary(fit.Bisect_Fracture) #estimated coefficients & p-value
```
From the output, the estimated intercept coefficent 0.029 correspond to the log odds of broke the bone with average days, in other words, on average days, expected probability of broke the bone is expit(0.029)=0.4927=49%.    
And one-unit increase in the predictor "days" increases the log odds of broke the bone(versus not broke the bone) by 0.0034.          
Further, p-value of days is 0.052 indicates that there is no strong evident but moderate evidence in support of the differences of the bone broke by the machine or not affected by drying time.       
```{r}
binnedplot(fitted(fit.Bisect_Fracture),resid(fit.Bisect_Fracture,type="response"))
```

Since the discrete residual plot does not tell us much about the model fit, we are using Binned residual plot for this model. Due to every points fall within the bounds, our model fits well in this case.

### Fracture like
Since "Fracture-like" is a binary outcomes(0 or 1) as well, therefore, as idea with above part, we used logistic regression to figure out their relationship.         
In addition, when "Fracture-like" is 0, it means the bone has no surface feature after cut by the standard fracturing machine, otherwise, it means fracturing machine made a mark on the bone.
```{r}
fit.Fracture_like<-glm(bone$`Fracture-like`~bone$days,family = binomial())
summary(fit.Fracture_like) #estimated coefficients, p-value
```
From the output, the estimated intercept coefficent 0.2551 correspond to the log odds of made a mark on bone with average days, in other words, on average days, expected probability of made a mark on bone is expit(0.2551)=0.436=43.6%.            
And one-unit increase in the predictor "days" increases the log odds of made a mark on bone(versus no surface feature on bone) by 0.0064.         
Also, p-value of days is 0.0055 indicates that there is strong evidence in determinging whether the bone has any surface feature after cut by the machine affected by drying time.     
```{r}
binnedplot(fitted(fit.Fracture_like),resid(fit.Fracture_like,type="response"))
```
Same logic with above part, our model fit well in this case.

### Fracture Angle
As "Fracture Angle" as no natural-order variable(nominal), since we cannot compare the order of angle of fresh bone and dry bone, and also N/A(non applicable) in this variable, so we used multinomial logit model in this case, that the outcome variable in this model has more than 2 levels.
```{r}
fit.Fracture_Angle<-multinom(bone$`Fracture Angle`~bone$days,trace = FALSE)
summary(fit.Fracture_Angle)
```
From the output, the baseline is Fracture Angle = Intermediate.    
A one-unit increase in the variable "days" is associated with the decrease in the log odds of being in Intermediate fracture angle vs. non applicable fracture angle in the amount of 0.0057.    
A one-unit increase in the variable "days" is associated with the decrease in the log odds of being in Intermediate fracture angle vs. oblique fracture angle in the amount of 0.003.    
In other words, if one-unit increase in "days", your chances of staying in the intermediate fracture angle category are higher compared to staying in non applicable and oblique.      
        
Since summary of multinomial logit model does not provide p-values, we can get significance of the coefficients by calculating z score and input it into the formula:    $z = (x_{i}-\bar{x})/s$ where coefficents of summary represents $x_{i}-\bar{x}$, and Std.Errors of summary represents$s$.       
```{r}
z <- summary(fit.Fracture_Angle)$coefficients / summary(fit.Fracture_Angle)$standard.errors
p <- (1-pnorm(abs(z),0,1)) * 2
p     # How to interpret significant part ??? 
```
From output, it represents p-value of coeffients. Only non applicable has strong evidence in determinging whether affected by drying time because of its p-value is 0.047 < 5%.        
```{r}
binnedplot(fitted(fit.Fracture_Angle),resid(fit.Fracture_Angle,type="response"))
```
It looks like our model fit kind of well in this case, but there might not good enough when expected values small.     

### Number of Fragments
Considering "Number of Fragments" as a numerical variable, we use the poisson regression at first. 

```{r,echo=T}
fit.Number_of_Fragments1 <- glm(bone$`Number of Fragments` ~ bone$days, family="poisson")
coef(fit.Number_of_Fragments1) #estimated coefficients
pchisq(fit.Number_of_Fragments1$deviance,df=fit.Number_of_Fragments1$df.residual, lower.tail=FALSE)
```
Here our null hypothesis is that our model is correctly specified. The low p-value shows that we can reject this hypothesis, thus the possion regression model fits poorly. Next, we consider to use a negative binomial model.
```{r,echo=F}
fit.Number_of_Fragments2 <- glm.nb(bone$`Number of Fragments` ~ bone$days)
summary(fit.Number_of_Fragments2)
pchisq(fit.Number_of_Fragments2$deviance,df=fit.Number_of_Fragments2$df.residual, lower.tail=FALSE)
```
Using the negative binomial model, we have a better fit. The only variable "days" has a coefficient of 0.002247, which is statistically significant. This means that for each one-unit increase in "days", the expected log count of the number of fragments increases by 0.002247.

### Fracture Outline
We assume "Fracture Outline" as no natural-order(nominal) variable, same reason as "Fracture Angle" part, thus we used multinomial logit model.
```{r}
fit.Fracture_Outline<-multinom(bone$`Fracture Outline`~bone$days,trace = FALSE)
coef(fit.Fracture_Outline) #estimated coefficients
```
From the output, the baseline is Fracture Angle = Cruved/Jagged.    
A one-unit increase in the variable "days" is associated with the decrease in the log odds of being in curved fracture outline vs. intermediate fracture outline in the amount of 0.0155.    
A one-unit increase in the variable "days" is associated with the decrease in the log odds of being in curved fracture outline vs. non applicable fracture outline in the amount of 0.0043.    
In other words, if one-unit increase in "days", your chances of staying in the curved/jagged fracture outline category are higher compared to staying in non applicable, intermediate and transverse.      
Get significance of the coefficients by calculating z score and input it into the formula:  

```{r}
z <- summary(fit.Fracture_Outline)$coefficients / summary(fit.Fracture_Outline)$standard.errors
p <- (1-pnorm(abs(z),0,1)) * 2
p
```
From output, it represents p-value of coeffients. Only the non applicable has strong evidence to determining whether it affected by drying time because of its p value is 0.017 < 5%.  

```{r}
binnedplot(fitted(fit.Fracture_Outline),resid(fit.Fracture_Outline,type="response"))
```
Looks like our model fit kind of well in this case, except there might not good enough when expected values really small. 

### Fractographic Features(Revise)
Since "Fractographic Features" is an no natural-order(nominal) variable, we used multinomial logit model as before.
```{r}
fit.Fractographic_Features<-multinom(bone$`Fractographic Features`~bone$days,trace = FALSE)
coef(fit.Fractographic_Features)   #compression curl == compressional curl 
```
From the output, the baseline is Fractographic Features = Arrest Ridge.    
A one-unit increase in the variable "days" is associated with the increase in the log odds of being in arrest ridge features vs. ibone hackle feature in the amount of 0.13.    
A one-unit increase in the variable "days" is associated with the decrease in the log odds of being in arrest ridge features vs. bone hackle, wake hackgle, arrest ridge feature in the amount of 0.0042.    
Same logic to interpret following coefficients.    
In other words, if one-unit increase in "days", your chances of staying in the arrest ridge features category are higher compared to staying in bone hackle, wake hackle, arrest ridge feature category; bone mirror feature; compression curl feature category and so on, except bone hackle feature and wake hackle with arrest ridge feature.      
Get significance of the coefficients by calculating z score and input it into the formula:     
```{r}
z <- summary(fit.Fractographic_Features)$coefficients / summary(fit.Fractographic_Features)$standard.errors
p <- (1-pnorm(abs(z),0,1)) * 2
p
```
From output, it represents p-value of coeffients. Only coefficients of "days" for bone hackle feature and wake hackle with arrest ridge feature category are significant because of 0.017 < 5%.      
```{r}
binnedplot(fitted(fit.Fractographic_Features),resid(fit.Fractographic_Features,type="response"))
``` 
From the plot, most of points fall left handside, and it may hard to see whether they fall inside the bounds or not. Therefore, the model might not good enough.              

# Conclusion




##Chi-square test for Independence

```{r}
tb.1 = table(bone$`WAKE HACKLE`, bone$`BONE HACKLE`) 
chisq.test(tb.1) 
tb.2 = table(bone$`WAKE HACKLE`, bone$`BONE MIRROR`) 
chisq.test(tb.2) 
tb.3 = table(bone$`WAKE HACKLE`, bone$`CANTILEVER CURL`) 
chisq.test(tb.3) 
tb.4 = table(bone$`WAKE HACKLE`, bone$`ARREST RIDGE`) 
chisq.test(tb.4) 
tb.5 = table(bone$`WAKE HACKLE`, bone$`WALLNER LINES`) 
chisq.test(tb.5) 
tb.6 = table(bone$`BONE HACKLE`, bone$`BONE MIRROR`) 
chisq.test(tb.6) 
tb.7 = table(bone$`BONE HACKLE`, bone$`CANTILEVER CURL`) 
chisq.test(tb.7) 
tb.8 = table(bone$`BONE HACKLE`, bone$`ARREST RIDGE`) 
chisq.test(tb.8) 
tb.9 = table(bone$`BONE HACKLE`, bone$`WALLNER LINES`) 
chisq.test(tb.9)
tb.10 = table(bone$`BONE MIRROR`, bone$`CANTILEVER CURL`) 
chisq.test(tb.10)
tb.11 = table(bone$`BONE MIRROR`, bone$`ARREST RIDGE`) 
chisq.test(tb.11)
tb.12 = table(bone$`BONE MIRROR`, bone$`WALLNER LINES`) 
chisq.test(tb.12)
tb.13 = table(bone$`CANTILEVER CURL`, bone$`ARREST RIDGE`) 
chisq.test(tb.13)
tb.14 = table(bone$`CANTILEVER CURL`, bone$`WALLNER LINES`) 
chisq.test(tb.14)
tb.15 = table(bone$`ARREST RIDGE`, bone$`WALLNER LINES`) 
chisq.test(tb.15)
```

## Logistic Regression for six feature v.s. days

```{r}
fit.Feature.1<-glm(bone$`WAKE HACKLE`~bone$days,family = binomial())
summary(fit.Feature.1)
binnedplot(fitted(fit.Feature.1),resid(fit.Feature.1,type="response"))
```

```{r}
fit.Feature.2<-glm(bone$`BONE HACKLE`~bone$days,family = binomial())
summary(fit.Feature.2)
binnedplot(fitted(fit.Feature.2),resid(fit.Feature.2,type="response"))
```

```{r}
fit.Feature.3<-glm(bone$`BONE MIRROR`~bone$days,family = binomial())
summary(fit.Feature.3)
binnedplot(fitted(fit.Feature.3),resid(fit.Feature.3,type="response"))
```

```{r}
fit.Feature.4<-glm(bone$`CANTILEVER CURL`~bone$days,family = binomial())
summary(fit.Feature.4)
binnedplot(fitted(fit.Feature.4),resid(fit.Feature.4,type="response"))
```

```{r}
fit.Feature.5<-glm(bone$`ARREST RIDGE`~bone$days,family = binomial())
summary(fit.Feature.5)
binnedplot(fitted(fit.Feature.5),resid(fit.Feature.5,type="response"))
```

```{r}
fit.Feature.6<-glm(bone$`WALLNER LINES`~bone$days,family = binomial())
summary(fit.Feature.6)
binnedplot(fitted(fit.Feature.6),resid(fit.Feature.6,type="response"))
```

```{r}
count_1 = 0
for (i in 1:nrow(bone)){
  if (bone$`WAKE HACKLE`[i]==1){
    count_1=count_1+1
  }
    
}
```

